\textbf{EECS 340: Assignment 2}

### 2020-02-02 assignment_2/article.tex
✨ Add sketch answer to Problem 1(d2) and (d3).

>>>>

\subsection{(d2) If $f(n) = O(n^c)$, then $f(2n) = O(n^c)$}

As It is known from \textbf{d1} that $f(2n) = \Theta(f(n))$, which implies $f(2n) = O(f(n))$. Also it is given that $f(n) = O(n^c)$. Together, we shall infer $f(2n) = O(n^c)$ due to the transitivity property of $\Theta$- and $O$-notations.

\subsection{(d3) If $f(n) = \Theta(n^c)$, then $f(2n) = \Theta(f(n))$}
Please refer to proof at \textbf{d3} as it provides a broader proof base on $f(n)$ regardless $f(n) = \Theta(n^c)$ or not.
